Adaptative neighbouring methods applied to telephonic base stations

### 2024-08-23 article.tex
Corrections légères de mise en page

\section{Introduction}
    \IEEEPARstart{T}{he} field of telecommunication represents a gigantic mine of information, the smartphone penetration rate being 69\% in 2023 in the world, and 97\% in France. Therefore, the collected datas represent a big opportunity for telecommunication companies to predict their customers behaviour for internal or marketing purposes.

@@

\section{Results\label{sec:res}}
    \subsection{Measurement of BS density}
        Each of the three methods for detecting the high density base stations that were described above detect the major cities of France. It is even possible to accurately detect the name of these cities by looking, for each cluster, at the most represented "nom\_com" field of the base station of the cluster.

        Morevover, the correlation coefficient between the number of inhabitant and the number of base station is above 0.9 for each of the methods.

@@

        When comparing the cluster detected to the cities that have more than 7000 inhabitants, 3-NN is the method that has the best result. In fact, if we consider all base station with a $\gamma_p$ value inferior to 2 km to be in cities we find that the percentage at accurately classified base station is 88\%. It is 87\% for DBScan and 85\% for HDBScan.

        Plus, as seen before, we can use the $\gamma_p$ value of the 3-NN method to classify each city in precise category, not only city vs coutryside.

        Here is the classification that has been chosen : 
        \begin{itemize}
            \item city center: $\gamma_p\in [0,1]$;
            \item urban area: $\gamma_p\in ]1,2]$;
            \item extra-urban: $\gamma_p\in ]2,4]$;
            \item countryside: $\gamma_p\in ]4,\infty[$.
        \end{itemize}

    \subsection{Best potential neighbours}
        First of all, the $k$-NN method could have provided a solution to the fact that the Delaunay triangulation does not connect all the points but makes choices. However, to obtain interesting connections, we need to choose a relatively high $k$, greater than 10, which implies a large number of connections and therefore an increase in   computational cost. What's more, applying the criteria doesn't even produce convincing results.

@@

    \subsection{Optimizing criteria parameters}
        As seen in Section~\ref{sec:contrib}, the angle and distance criteria must adapt their threshold to the density of base station. The chosen thresholds for each of the previously introduced categories are presented in Table~\ref{table:crit_summary}. if both potential neighbours are in a different category, then the higher threshold is chosen.
g
        \begin{table}
            \centering
            \caption{Summary of criteria values.}
            \label{table:crit_summary}
            \begin{tabular}{lcc}
                \toprule
                \textbf{Description} & \textbf{\emph{max\_distance}} & \textbf{\emph{min\_angle}} \\
                \cmidrule(lr){1-3}
                city center & $\unit[2]{km}$ & $5^\circ$ \\
                urban area & $\unit[5]{km}$ & $10^\circ$ \\
                extra-urban area & $\unit[10]{km}$ & $15^\circ$ \\
                countryside & $\unit[15]{km}$ & $20^\circ$ \\
                \bottomrule
            \end{tabular}
        \end{table}

@@

        In the future, there will be method to compare our results with a reference. [pas sûr si on garde ca]
        \begin{figure}
            \centering
            \includegraphics[width=3.5in]{images/illus_graphs/final_neighs_del_da.png}
            \caption{The final neighbouring graph.}
            \label{fig:final_neighs}
        \end{figure}

>>>>

\section{Introduction}
    \IEEEPARstart{T}{he} field of telecommunication represents a gigantic mine of information, the smartphone penetration rate being $69\%$ in 2023 in the world, and $97\%$ in France. Therefore, the collected datas represent a big opportunity for telecommunication companies to predict their customers behaviour for internal or marketing purposes.

@@

\section{Results\label{sec:res}}
    \subsection{Measurement of BS density}
        Each of the three methods for detecting the high density base stations that were described above detect the major cities of France. It is even possible to accurately detect the name of these cities by looking, for each cluster, at the most represented \textsl{nom\_com} field of the base station of the cluster.

        Morevover, the correlation coefficient between the number of inhabitant and the number of base station is above $0.9$ for each of the methods.

@@

        When comparing the cluster detected to the cities that have more than $7\,000$ inhabitants, $3$-NN is the method that has the best result. In fact, if we consider all base station with a $\gamma_p$ value inferior to $\unit[2]{km}$ to be in cities we find that the percentage at accurately classified base station is $88\%$. It is $87\%$ for DBScan and $85\%$ for HDBScan.

        Plus, as seen before, we can use the $\gamma_p$ value of the $3$-NN method to classify each city in precise category, not only city vs coutryside.

        Here is the classification that has been chosen: 
        \begin{itemize}
            \item city center: $\gamma_p\in [0,1]$;
            \item urban area: $\gamma_p\in ]1,2]$;
            \item extra-urban: $\gamma_p\in ]2,4]$;
            \item countryside: $\gamma_p\in ]4,\infty[$.
        \end{itemize}

    \subsection{Best potential neighbours}
        First of all, the $k$-NN method could have provided a solution to the fact that the Delaunay triangulation does not connect all the points but makes choices. However, to obtain interesting connections, we need to choose a relatively high $k$, greater than $10$, which implies a large number of connections and therefore an increase in   computational cost. What's more, applying the criteria doesn't even produce convincing results.

@@

    \subsection{Optimizing criteria parameters}
        As seen in Section~\ref{sec:contrib}, the angle and distance criteria must adapt their threshold to the density of base station. The chosen thresholds for each of the previously introduced categories are presented in Table~\ref{table:crit_summary}. if both potential neighbours are in a different category, then the higher threshold is chosen.
        \begin{table}
            \centering
            \caption{Summary of criteria values.}
            \label{table:crit_summary}
            \begin{tabular}{lcc}
                \toprule
                \textbf{Description} & \textbf{\emph{max\_distance}} & \textbf{\emph{min\_angle}} \\
                \cmidrule(lr){1-3}
                city center & $\unit[2]{km}$ & $5^\circ$ \\
                urban area & $\unit[5]{km}$ & $10^\circ$ \\
                extra-urban area & $\unit[10]{km}$ & $15^\circ$ \\
                countryside & $\unit[15]{km}$ & $20^\circ$ \\
                \bottomrule
            \end{tabular}
        \end{table}

@@

        In the future, there will be method to compare our results with a reference.
        \begin{figure}
            \centering
            \includegraphics[width=3.5in]{images/illus_graphs/final_neighs_del_da.png}
            \caption{The final neighbouring graph.}
            \label{fig:final_neighs}
        \end{figure}
